OptiFit GLNE Exploratory

### 2022-01-28 exploratory/exploratory.Rmd
updated exploratory doc

```{r mcc}
merged_mcc <- read_csv("../data/learning/summary/merged_MCC.csv") %>% 
  mutate(label = case_when(algorithm == "opticlust" ~ algorithm,
                           TRUE ~ paste0(algorithm,"_",subset))) %>% 
  mutate(color=case_when(algorithm == "opticlust" ~ "OptiClust",
                         subset == "train" ~ "OptiFit Reference",
                         state == "fit" ~ "Optifit Fit without Reference",
                         TRUE ~ "Optifit Fit with Reference")) %>% 
  mutate(label = factor(label,levels=c("opticlust","optifit_train","optifit_test"),
                        labels = c("OptiClust","OptiFit Train","OptiFit Test")))

merged_mcc %>% 
  ggplot(aes(x=label,y=mcc,color=color)) +
    geom_jitter(height=0,width=0.2,alpha=0.5,size=3) +
    theme_bw() +
    xlab("") + ylab("MCC") +
    theme(panel.grid.major.y = element_line(color="grey85"),
          panel.grid.minor.y = element_line(color="grey85"),
          panel.grid.major.x = element_blank()) +
    geom_text(aes(label,mcc,label=split),data=subset(merged_mcc, mcc < 0.7),color="black",hjust=0) #+
    # geom_text(aes(label,mcc,label=split),data=subset(merged_mcc, split == lowest_pct_mapped),color="black",hjust=0) +
    # geom_text(aes(label,mcc,label=split),data=subset(merged_mcc, split == highest_pct_mapped),color="black",hjust=0)

>>>>

```{r mcc}
merged_mcc <- read_csv("../data/learning/summary/merged_MCC.csv") %>% 
  mutate(label = case_when(algorithm == "opticlust" ~ algorithm,
                           TRUE ~ paste0(algorithm,"_",subset))) %>% 
  mutate(Group=case_when(algorithm == "opticlust" ~ "OptiClust",
                         subset == "train" ~ "OptiFit Reference",
                         state == "fit" ~ "Optifit Fit without Reference",
                         TRUE ~ "Optifit Fit with Reference")) %>% 
  mutate(label = factor(label,levels=c("opticlust","optifit_train","optifit_test"),
                        labels = c("OptiClust","OptiFit Train","OptiFit Test")))

merged_mcc %>% 
  ggplot(aes(x=label,y=mcc,color=Group)) +
    geom_jitter(height=0,width=0.2,alpha=0.5,size=3) +
    theme_bw() +
    xlab("") + ylab("MCC") +
    theme(panel.grid.major.y = element_line(color="grey85"),
          panel.grid.minor.y = element_line(color="grey85"),
          panel.grid.major.x = element_blank()) +
    geom_text(aes(label,mcc,label=split),data=subset(merged_mcc, mcc < 0.7),color="black",hjust=0) #+
    # geom_text(aes(label,mcc,label=split),data=subset(merged_mcc, split == lowest_pct_mapped),color="black",hjust=0) +
    # geom_text(aes(label,mcc,label=split),data=subset(merged_mcc, split == highest_pct_mapped),color="black",hjust=0)

```
```{r opticlust_20_mcc}

opticlust_20_mcc <- read_csv("../results/tables/opticlust_20_mcc.csv") %>% 
  mutate(Group="OptiClust 20%")

merged_mcc %>% 
  filter(algorithm=="optifit",subset=="test") %>% 
  select(mcc,split,algorithm,Group) %>% 
  bind_rows(opticlust_20_mcc) %>% 
  ggplot(aes(x=algorithm,y=mcc,color=Group)) +
    geom_jitter(height=0,width=0.2,alpha=0.5,size=3) +
    theme_bw() +
    xlab("") + ylab("MCC") +
    theme(panel.grid.major.y = element_line(color="grey85"),
          panel.grid.minor.y = element_line(color="grey85"),
          panel.grid.major.x = element_blank())
